KidsAIR: Main analysis

### 2020-12-09 main_analysis_final.Rmd
main analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 7 Dec 2020"
output: pdf_document
---

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))
```

@@

itt_winter1_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter1, family = binomial, nAGQ = 20)
write_rds(itt_winter1_results, paste0(file_path, "Output/itt_winter1_results.rds"))

itt_winter2_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter2, family = binomial, nAGQ = 20)
write_rds(itt_winter2_results, paste0(file_path, "Output/itt_winter2_results.rds"))

itt_noak_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data_noak, family = binomial, nAGQ = 20)
write_rds(itt_noak_results, paste0(file_path, "Output/itt_noak_results.rds"))

itt_income_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + income_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_income_results, paste0(file_path, "Output/itt_income_results.rds"))

itt_filter_type_results <- glmer(lrti_events_di_total ~ treatment_filter_type +  
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_filter_type_results, paste0(file_path, "Output/itt_filter_type_results.rds"))

itt_filter_comp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + kw_perc_exp_cat2 + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

itt_smoke_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + residents_smoke + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_smoke_results, paste0(file_path, "Output/itt_smoke_results.rds"))

itt_burn_level_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + burn_level_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_burn_level_results, paste0(file_path, "Output/itt_burn_level_results.rds"))

itt_smoking_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_smoking_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_smoking_results, paste0(file_path, "Output/itt_smoking_results.rds"))

itt_windows_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_windows_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_windows_results, paste0(file_path, "Output/itt_windows_results.rds"))

itt_door_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_door_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_door_results, paste0(file_path, "Output/itt_door_results.rds"))

itt_sweep_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_sweep_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_sweep_results, paste0(file_path, "Output/itt_sweep_results.rds"))

itt_ambpm_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_pm_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_ambpm_results, paste0(file_path, "Output/itt_ambpm_results.rds"))

itt_ambtemp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_temp_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_ambtemp_results, paste0(file_path, "Output/itt_ambtemp_results.rds"))

itt_home_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_home_results, paste0(file_path, "Output/itt_home_results.rds"))

itt_outlier_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data_outliers, family = binomial, nAGQ = 20)
write_rds(itt_outlier_results, paste0(file_path, "Output/itt_outlier_results.rds"))
```

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
itt_noak_results <- read_rds(paste0(file_path, "Output/itt_noak_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_ambpm_results <- read_rds(paste0(file_path, "Output/itt_ambpm_results.rds"))
itt_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_ambtemp_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
itt_noak_tidy <- results_function(itt_noak_results, "ITT no AK")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_ambpm_tidy <- results_function(itt_ambpm_results, "ITT + amb PM")
itt_ambtemp_tidy <- results_function(itt_ambtemp_results, "ITT + amb temp")
itt_home_tidy <- results_function(itt_home_results, "ITT - home")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, itt_filter_comp_tidy,
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy,
                              itt_home_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT - home", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Primary = Logistic regression mixed model, as specified above  
ITT Winter 1 = Primary model with Winter 1 data only  
ITT no AK = Primary model without homes from AK (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT - home = Primary model without home as random term  
ITT outlier = Primary model with data that fixes incidence outlier

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + child_age + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
```

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_noak_tidy, itt_pm_income_tidy, itt_pm_filter_comp_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT no AK", "ITT + income", "ITT + filt comp", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 9 Dec 2020"
output: pdf_document
---

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))

#table(model.frame(itt_results)$treatment_assigned)
#nobs(itt_results)
```

@@

itt_winter1_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(itt_winter1_results, paste0(file_path, "Output/itt_winter1_results.rds"))

itt_winter2_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter2, family = binomial, nAGQ = 10)
write_rds(itt_winter2_results, paste0(file_path, "Output/itt_winter2_results.rds"))

itt_filter_type_results <- glmer(lrti_events_di_total ~ treatment_filter_type + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)

summary(itt_filter_type_results)

tidy_results <- tidy(itt_filter_type_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_filter_type", "", term),
         model = "Filter type") %>% 
  mutate(estimate = round(estimate, digits = 2),
         conf.low = round(conf.low, digits = 2),
         conf.high = round(conf.high, digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

table(model.frame(itt_filter_type_results)$treatment_filter_type)

analysis_check <- analysis_data %>% 
  mutate(pm_na = if_else(!is.na(pm_mean_sampling_period), "PM Yes", "PM Missing"))

save_table <- table(analysis_check$pm_na, analysis_check$lrti_events_di_total, analysis_check$treatment_filter_type)
save_table
ftable(save_table, 1)

write_rds(itt_filter_type_results, paste0(file_path, "Output/itt_filter_type_results.rds"))

itt_noak_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data_noak, family = binomial, nAGQ = 10)
write_rds(itt_noak_results, paste0(file_path, "Output/itt_noak_results.rds"))

itt_income_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + income_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_income_results, paste0(file_path, "Output/itt_income_results.rds"))

itt_filter_comp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + kw_perc_exp_cat2 + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

itt_smoke_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + residents_smoke + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_smoke_results, paste0(file_path, "Output/itt_smoke_results.rds"))

itt_burn_level_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + burn_level_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_burn_level_results, paste0(file_path, "Output/itt_burn_level_results.rds"))

itt_smoking_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_smoking_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_smoking_results, paste0(file_path, "Output/itt_smoking_results.rds"))

itt_windows_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_windows_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_windows_results, paste0(file_path, "Output/itt_windows_results.rds"))

itt_door_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_door_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_door_results, paste0(file_path, "Output/itt_door_results.rds"))

itt_sweep_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_sweep_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_sweep_results, paste0(file_path, "Output/itt_sweep_results.rds"))

itt_ambpm_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_pm_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_ambpm_results, paste0(file_path, "Output/itt_ambpm_results.rds"))

itt_ambtemp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_temp_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_ambtemp_results, paste0(file_path, "Output/itt_ambtemp_results.rds"))

itt_home_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_home_results, paste0(file_path, "Output/itt_home_results.rds"))

itt_outlier_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data_outliers, family = binomial, nAGQ = 10)
write_rds(itt_outlier_results, paste0(file_path, "Output/itt_outlier_results.rds"))
```

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
itt_noak_results <- read_rds(paste0(file_path, "Output/itt_noak_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
#itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_ambpm_results <- read_rds(paste0(file_path, "Output/itt_ambpm_results.rds"))
itt_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_ambtemp_results.rds"))
#itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
itt_noak_tidy <- results_function(itt_noak_results, "ITT no AK")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
#itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_ambpm_tidy <- results_function(itt_ambpm_results, "ITT + amb PM")
itt_ambtemp_tidy <- results_function(itt_ambtemp_results, "ITT + amb temp")
#itt_home_tidy <- results_function(itt_home_results, "ITT - home")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy,
                              itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Primary = Logistic regression mixed model, as specified above  
ITT Winter 1 = Primary model with Winter 1 data only  
ITT no AK = Primary model without homes from AK (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT outlier = Primary model with data that fixes incidence outlier

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
# Adding the randomization variable for child_age leads to the exact same model results
# Adding a random term for home adversely impacts the model since there is only one
# distinct observation per home

#table(model.frame(itt_pm_results)$treatment_assigned)
#nobs(itt_pm_results)
```

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
#itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
#itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
#itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_noak_tidy, itt_pm_income_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates
